Cybercrime and Online Video Games

### 2019-12-13 paper/paper.tex
Update paper.tex
Delete paper.pdf since it generates, add my introduction changes for real

[INTRODUCE ONLINE VIDEO GAMES; TALK ABOUT SUCCESS AND LARGE APPEAL]

[INTRODUCE CONCEPT OF HACKER FORUMS]

@@

% this is not compiling

% \begin{figure}
% \centering
% \begin{subfigure}{.5\textwidth}
% 	\centering
% 	\includegraphics[width = .4\linewidth]{Thread Count}
% 	\caption{Thread Count}
% \end{subfigure}
% \begin{subfigure}{.5\textwidth}
% 	\centering
% 	\includegraphics[width=.4\linewidth]{Comment Count}
% 	\caption{Comment Count}
% \end{subfigure}
% \caption{Thread and Comment Pie Charts}
% \label{fig:thread and comment charts}
% \end{figure}

>>>>

Since their inception decades ago, video games have become hugely preavalent in
society. Millions of people play video games as a hobby, and their demographics
span all age groups, ethnicities, and socioeconomic class. In particular, online
multiplayer video games have become hugely popular. Many of these games are 
highly competitive, and there any many players who look for unfair advantages in
the form of video game cheats. Video game cheats give the player abilities to 
to outperform their opponents. This competitive milieu has led to the
development of thriving marketplaces and economies devoted to creation and 
distribution of video game cheats. Online hacker forums are places where 
interested parties can sell, discuss, and review video game cheats. However, 
these vendors not only sell cheats but also online video game accounts. These
are especially desirable to perons who have been forbidden from playing an 
online game by the developers - usually for cheating or other malicious
behavior. Often, these accounts are stolen from innocent users and sold to 
malicious actors. Many of the players of online video games are 
children, and thus they are often the victims of account theft. This paper 
explores the crimware economy devoted to "Fortnite: Battle Royale."

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width = .4\linewidth]{ThreadCount}
	\caption{Thread Count}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width=.4\linewidth]{CommentCount}
	\caption{Comment Count}
\end{subfigure}
\caption{Thread and Comment Pie Charts}
\end{figure}
